RDF Validation Requirements - Evaluation and Logical Underpinning

### 2015-01-13 paper/RDF validation requirements/RDF validation requirements.tex
small touches

\begin{abstract}
There are many case studies for which the formulation of RDF constraints and the validation of RDF data conforming to these constraint is very important.  
The W3C and the DCMI working groups on RDF validation identified many RDF validation requirements,
whereupon we initiate an RDF validation requirements database which is available to contribute at \url{http://purl.org/net/rdf-validation}.
The intention of this database is to collaboratively collect case studies, use cases, requirements, and solutions regarding RDF validation.
Although, there are multiple constraint languages which can be used to formulate RDF constraints (associated with these requirements), 
there is no standard way to formulate RDF constraints.

This paper serves to evaluate to which extend each requirement is satisfied by each of these constraining languages.
We take reasoning into account as a pre-validation step and distinguish between OWL 2 QL and OWL 2 DL constructs to express particular constraints.
We classify constraints according to a developed classification mechanism for constraints.
We show that each constraint can be mapped to an ontology describing RDF constraints generically.
If a constraint can be expressed in DL, we add the mapping to DL and to the generic constraint in order to logically underpin associated requirements.
If a constraint cannot be expressed in DL, we only add the mapping to the generic constraint.

@@

The purpose of ontologies is to perform reasoning on RDF data and not to validate RDF data conforming to these ontologies.
For RDF, we cannot use ontologies like we use XML Schemas, DTDs, RELAX NG, or Schematron to validate XML documents.
The W3C organized the RDF Validation Workshop\footnote{\url{http://www.w3.org/2012/12/rdf-val/}}, 
where experts from industry, government, and academia discussed first use cases for RDF constraint formulation and validation.
In 2014, two working groups on RDF validation have been established: 
the W3C RDF Data Shapes WG\footnote{\url{http://www.w3.org/2014/rds/charter}} and the DCMI RDF Application Profiles WG\footnote{\url{http://wiki.dublincore.org/index.php/RDF-Application-Profiles}}.

>>>>

\begin{abstract}
There are many case studies for which the formulation of RDF constraints and the validation of RDF data conforming to these constraint is very important.  
The W3C and the DCMI working groups on RDF validation identified many RDF validation requirements. To collaboratively collect case studies, use cases, requirements, and solutions regarding RDF validation, we initiated a publicly open database of RDF validation requirements  (\url{http://purl.org/net/rdf-validation}).
The intention of this database .
Although, there are multiple constraint languages which can be used to formulate RDF constraints (associated with these requirements), 
there is no standard way to formulate RDF constraints.

This paper serves to evaluate to which extend each requirement is satisfied by each of these constrain languages.
We take reasoning into account as a pre-validation step and distinguish between OWL 2 QL and OWL 2 DL constructs to express particular constraints.
We classify constraints according to a developed classification mechanism for constraints.
We show that each constraint can be mapped to an ontology describing RDF constraints generically.
If a constraint can be expressed in DL, we add the mapping to DL and to the generic constraint in order to logically underpin associated requirements.
If a constraint cannot be expressed in DL, we only add the mapping to the generic constraint.

@@

The W3C organized the RDF Validation Workshop\footnote{\url{http://www.w3.org/2012/12/rdf-val/}}, 
where experts from industry, government, and academia discussed first use cases for RDF constraint formulation and validation.
In 2014, two working groups on RDF validation have been established: 
the W3C RDF Data Shapes WG\footnote{\url{http://www.w3.org/2014/rds/charter}} and the DCMI RDF Application Profiles WG\footnote{\url{http://wiki.dublincore.org/index.php/RDF-Application-Profiles}}.
